working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-05 Manuscript_draft/Manuscript_draft.Rmd
Edits

>>>>

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=6,fig.cap="A"}

load("effect_size_species/effect_size_total.RData")

 ggplot(all, aes(Family,Cohen_d,colour=Family_1), size=10) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = "italic"))+ geom_point( aes(colour=Family_1),size=2) +
  geom_errorbar(aes(x = Family, ymin = Lower, 
ymax = Upper,colour=Family_1), width = 0.2, size=0.8)+
  scale_color_manual(name  ="Family",values=c( "#0072B2", "#009E73", "#D55E00"), labels=c("Solanaceae", "Convolvulaceae","Brassicaceae"))+
  scale_fill_manual(name  ="Family",values=c( "#0072B2", "#009E73", "#D55E00"), labels=c("Solanaceae", "Convolvulaceae","Brassicaceae"))+
  xlab("") + ylab("Cohen's d") + rotate()+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+scale_alpha(guide = 'none')
```
